Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-27 article.tex
bookmark

%An infinitesimal volume contains aerosols. The extinction and
%scattering coefficients due to aerosols in this volume are,
%respectively
%\begin{equation}
%  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
%  \;\;,\;\;
%  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
%  \;.
%  \label{eq:betaer}
%\end{equation}
%The infinitesimal volume contain also air molecules. Hence, the
%overall extinction and scattering coefficients in this small volume
%are, respectively
%\begin{equation}
%  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
%  \;\;,\;\;
%  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
%  \;.
%  \label{eq:betair}
%\end{equation}

@@

Scattering by air molecules follows the
{\em Rayleigh} model. The phase function is
\begin{align}
  P^{\rm air}\left[\mu\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and the single scattering albedo in visible light is $\varpi^{\rm air}$=1. Air molecular density falls off approximately exponentially with altitude $h$, with a characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Thus~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules can be modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4}
  \exp(-h/H^\mathrm{air})
  \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}
where $\lambda$ is the wavelength, in microns.

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

Monte Carlo (MC) methods enable rigorous modeling of photon
propagation in the atmosphere. The radiative transfer is expressed as
probability distributions which describe the distance travelled by the
photon between scatterings and the angle of deflection at each
scatter.  This enables simulating multiple scattering and produce
realistic results.  MC simulations can be made arbitrarily accurate by
increasing the number of photons.  Another advantage of the MC methods
is that they are highly parallelizable.

The MC simulations use the same atmosphere grid described in
\cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
traced from the detector to the sun. Photons are emitted from each
pixel of the camera in the direction determined by the camera
model. The optical distance that the photon travels before scattering
is determined according to the Beer-Lambert law~\cref{eq:beer-lambert}
and the inversion sampling method. Once the optical distance is
determined the ``real'' distance is determined by summing the optical
depth of the discrete voxels (\cref{sec:optical-depth}) along the
photon direction till the desired optical distance is reached.  At
each scattering event, first the type of aerosol is determined by
sampling the different aerosols distributions inside the voxel. The
new direction is determined by inverse sampling the phase function of
the relevant aerosols: Rayleigh, \cref{eq:rayleighP} or
Henyey-Greenstein \cref{eq:aerosol_scatter}.  To accelerate the MC we
use the local estimation (LE) method.

@@

\noindent{\bf Dimensions}: The domain of sky we simulate and recover
has area of \SI{50 x 50}{\km}, and it extends from the ground up to
altitude of \SI{10}{\km}. This volume is divided into a rectilinear
grid. We used different grid sizes from \num{50 x 50 x 100} grid,
where each voxel has area of \SI{1 x 1}{\km} and vertical thickness of
\SI{100}{\metre} and down to num{10 x 10 x 20} grid, where each voxel
has area of \SI{5 x 5}{\km} and vertical thickness of
\SI{500}{\metre}. The different grid sizes determine the number of
variables.

@@

\noindent{\bf Cameras}: The cameras are created by the MC simulations.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).
    [c] Cross section along the
  }
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.

>>>>

% An infinitesimal volume contains aerosols. The extinction and
% scattering coefficients due to aerosols in this volume are,
% respectively
% \begin{equation}
%  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
%  \;\;,\;\;
%  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
%  \;.
%  \label{eq:betaer}
%\end{equation}
%The infinitesimal volume contain also air molecules. Hence, the
% overall extinction and scattering coefficients in this small volume
% are, respectively
% \begin{equation}
%  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
%  \;\;,\;\;
%  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
%  \;.
%  \label{eq:betair}
%\end{equation}

@@

Scattering by air molecules follows the {\em Rayleigh} model. The
phase function is
\begin{align}
  P^{\rm air}\left[\mu\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and the single scattering albedo in visible light is $\varpi^{\rm
  air}$=1. Air molecular density falls off approximately exponentially
with altitude $h$, with a characteristic~\cite{Levi1980} falloff
height $H^\mathrm{air}=8\ \si{\km}$. Thus~\cite{Levi1980}, the
coefficients for extinction and scattering by air molecules can be
modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4} \exp(-h/H^\mathrm{air})
  \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}
where $\lambda$ is the wavelength, in microns.
\\

\noindent {\bf Inverse Transform Sampling}: Monte Carlo methods
simulate probabilistic phenomena by sampling from their probability
disrtibutions.  Inverse transform sampling~\cite{devroye1986sample} is a common method for generating
sample numbers at random from any probability distribution given its
cumulative distribution function (cdf).  Let $X$ be a random variable
whose distribution can be described by the cumulative distribution
function $F$.  First we generate a random number $u$ from the standard
uniform distribution in the interval $[0,1]$.  Then to draw a random
number from the distribution described by $F$ we need to calculate the
value $x$ such that $x = F^{-1}(u)$.

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).
    [c] Cross section along the
  }
  \label{fig:simulation-results1}
\end{figure}

@@

Monte Carlo (MC) methods enable rigorous modeling of photon
propagation in the atmosphere. The radiative transfer is expressed as
probability distributions which describe the distance travelled by the
photon in-between scatterings and the angle of deflection at each
scatter.  This enables simulating multiple scattering and produce
realistic results.  MC simulations can be made arbitrarily accurate by
increasing the number of photons.  Another advantage of the MC methods
is that they are highly parallelizable.

The MC simulations use the same atmosphere grid described in
\cref{sec:single-scatt-model}. we use backward MC, i.e. photons are
traced from the detector, camera, to their source, sun. Photons are
emitted from each pixel of the camera in the direction determined by
the camera model, i.e. hemispherical camera. The quality of the
simulations is proportional to the number of photons. To create the
\cref{fig:simulation-results1}b \num{10000} photons were emitted from
each pixel. The distance travelled by the photon till its first
scattering is determined by inversion sampling the transmittance
probability (\cref{sec:theor-backgr}) optical distance
distribution. This is done using the inversion sampling method. Once
the optical distance is determined the ``real'' distance is determined
by summing the optical depth of the discrete voxels
(\cref{sec:optical-depth}) along the photon direction till the desired
optical distance is reached.  At each scattering event, first the type
of aerosol is determined by sampling the different aerosols
distributions inside the voxel. The new direction is determined by
inverse sampling the phase function of the relevant aerosols:
Rayleigh, \cref{eq:rayleighP} or Henyey-Greenstein
\cref{eq:aerosol_scatter}.  To accelerate the MC we use the local
estimation (LE) method.

@@

\noindent{\bf Dimensions}: The domain of sky we simulate and recover
has area of \SI{50 x 50}{\km}, and it extends from the ground up to
altitude of \SI{10}{\km}. This volume is divided into a rectilinear
grid. We used different grid sizes from \num{50 x 50 x 100} grid,
where each voxel has area of \SI{1 x 1}{\km} and vertical thickness of
\SI{100}{\metre} and down to \num{10 x 10 x 20} grid, where each voxel
has area of \SI{5 x 5}{\km} and vertical thickness of
\SI{500}{\metre}. The different grid sizes determine the number of
variables.

@@

\noindent{\bf Cameras}: The acquired images are cresimulated using the the MC model.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.
